A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
fpp text in

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to three major factors.  First, the superior precision
of the \kepler\ photometry enables detection of secondary stellar
eclipses, odd-even transit depth variations, and ellipsoidal
variations \citep{Batalha:2010} to a much lower level than
ground-based surveys. Second, the relatively small pixels and stable
pointing of the \kepler\ telescope has enabled the identification of
many spatially distinct blended eclipsing binaries by means of
detailed pixel-level analysis \citep{Bryson:2013} to identify shifts
in the center of light during transits.  And finally, \kepler\ is
sensitive to much smaller planets than ground-based surveys, and it
turns out that small planets are much more common than hot Jupiters.

In \KT, the precision of these tests is lower and they must be applied
with care.  There are typically only a handful of transits, meaning
differences between ``odd'' and ``even'' transits must be large to
create a significant difference. Searching for ellipsoidal variations
is hindered by the short time baseline and the increased photometric
uncertainty in \KT\ data.  Centroid variations are feasible in
\KT\ but must be treated differently than in the original
\kepler\ mission where this effect was generally measured using
difference imaging \citep{Batalha:2010}.

@@

A quick \emph{a priori} estimate of the background blended ecipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that something close to
$\sim$10\% of stars might host close binary companions within the
period range accessible by this survey, this gives a probability of
0.016 that a blended binary star might be chance-aligned within two
pixels of any given target star.  Noting that the average number of
planets per star with periods less than 30 days is about 0.25
\citep{Fressin:2013}, we can roughly estimate that we expect $<$10\%
of our candidates to be caused by nearby contaminating EBs.  This
estimate suggests that such astrophsycial false positives should be
rare in our sample, consistent with our detection of 2/36 candidates
with clear centroid offsets.

>>>>

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to three major factors.  First, the superior precision
of the \kepler\ photometry enables detection of secondary stellar
eclipses, odd-even transit depth variations, and ellipsoidal
variations \citep{Batalha:2010} to a much lower level than
ground-based surveys. Second, the relatively small pixels and stable
pointing of the \kepler\ telescope has enabled the identification of
many spatially distinct blended eclipsing binaries by means of
detailed pixel-level analysis \citep{Bryson:2013} to identify shifts
in the center of light during transits.  And finally, \kepler\ is
sensitive to much smaller planets than ground-based surveys, and small
planets are much more common than the Jupiter-sized planets able to be
detected from the ground.

In \KT, the precision of the photometric tests used to vet for such
false positives  is lower and they must be applied
with care.  There are typically only a handful of transits, meaning
differences between ``odd'' and ``even'' transits must be large to
create a significant difference. Searching for ellipsoidal variations
is hindered by the short time baseline and the increased photometric
uncertainty in \KT\ data.  Centroid variations are feasible in
\KT\ but must be treated differently than in the original
\kepler\ mission where this effect was generally measured using
difference imaging \citep{Batalha:2010, Bryson:2013}.

@@

A quick \emph{a priori} estimate of the background blended ecipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that $\sim$10\% of stars
might host close binary companions within the period range accessible
by this survey, this gives a probability of 0.016 that a blended
binary star might be chance-aligned within two pixels of any given
target star.  Noting that the average number of planets per star with
periods less than 30 days is about 0.25 \citep{Fressin:2013}, we can
roughly estimate that we expect $<$10\% of our candidates to be caused
by nearby contaminating EBs.  This estimate suggests that such
astrophsycial false positives should be rare in our sample, consistent
with our detection of 2/36 candidates with clear centroid offsets.
